### 2021-07-19 doc/thesis/chapters/system-design-process.tex
investigate alternatives

The problem statement is updated and improved by the re-evaluate step, which is described later.

@@

>>>>

The problem statement is updated and improved by the Re-evaluate step, which is described later.

@@

In almost any kind of problem, there are multiple ways in order to archieve a successful solution.
However, some solutions may be preferred over others because of certain criteria that are evaluated.
Such criteria may be cost, risk, schedule or performance.
Based on the combined evaluation of these factors, a decision in favor of one selected alternative is made.\\

It is important to note that this step is a repeated step.
This is necessary, since there may only be a few known facts available at the initial intestigation.
Further design steps, such as a first estimation of the intended design implementation, simulation results, or a prototype can provide more data and facts.
These can be used to re-evaluate the alternatives and consequently optimize the design process.
